\documentclass[12pt]{article}
\usepackage{graphicx}
% \usepackage[section]{placeins}
% \usepackage[a4paper,margin=0.75in]{geometry}
% \usepackage{array}
% \usepackage{varwidth}
% \usepackage{tabularx}
% \usepackage{amsmath}
% \usepackage{subcaption}
% \usepackage{svg}

\graphicspath{{images/}}

\title{NCERT Physics Questions \\ Chapter 11: Sound}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Theory questions}
\subsection*{Short theory questions}
\begin{enumerate}
	\item What is a medium for sound?
	\item What is a wave in a medium?
	\item What is the meaning of a mechanical wave? Give example of \\ mechanical and non mechanical wave.
	\item Give the three characteristics of a sound wave.
	\item Define wavelength and give its SI unit.
	\item Formal definition of one oscillation of a sound wave.
	\item Define frequency and give its SI unit.
	\item What is time period of a wave.
	\item Formula relation between frequency and time period of a wave.
	\item What is pitch of a sound wave?
	\item Define amplitude of a wave and its unit.
	\item What is loudness? What does the definition of loudness and pitch have in common?
	\item What is a tone and a note? How is it different from noise?
	\item Another name for sound quality. Also give an informal definition of quality of a sound.
	\item Give the formula of speed of sound using a) Time period, b) frequency.
	\item Define intensity of sound.
	\item Give the two properties that speed of sound depends on.
	\item State the law of reflection of sound.
	\item What is the time delay between sound reflections for our brains to register it as a separate echo?
	\item What is reverberation and how do we reduce it?
	\item Audible range of sound for the average human.
	\item What is infrasound and ultrasound, and give some real world examples for each.
	\item What is echocardiography?
	\item Explain ultrasonography.
\end{enumerate}

\subsection*{Long theory questions}
\begin{enumerate}
	\item Explain the propogation of sound in terms of
	\begin{enumerate}
		\item its effect on each particle in the medium.
		\item pressure differences in the medium.
	\end{enumerate}
	\item Definition and difference between longtitudinal wave and transverse wave.
	\item Define the peak and trough of a wave.
	\item Give the difference between amplitude, intensity, and loudness of a sound wave. Are they related to one another?
	\item Give 3 uses of reflection of sound to our advantage.
	\item \textit{(very big)} Briefly explain each of the five applications of ultrasound.
\end{enumerate}

% \section*{Statement problems}
% \begin{enumerate}
% \end{enumerate}

% \section*{Numericals}
% \subsection*{Hard}
% \begin{enumerate}
% \end{enumerate}

\end{document}
